---
title: "Analyzing Factors Influencing GDP"
# author: "Badar, Divya, Dilpa, Inshal, Shahzeb, Tayyab"
# date: "November 23, 2019"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
    orientation: rows
---

``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r setup, include=FALSE}
library(flexdashboard) # Dashboard package
library(highcharter) # Interactive data visualizations
library(plotly) # Interactive data visualizations
library(viridis) # Color gradients
library(tidyverse) # Metapackge
library(countrycode) # Converts country names/codes
library(rjson) # JSON reader
library(crosstalk) # Provides interactivity for HTML widgets
library(DT) # Displaying data tables
library(plyr)
library(treemap) #For Treemap
library(viridisLite)#For color maps in R
```

```{r include=FALSE}
data <- read.csv('CIA Factsheet 2013.csv')
names(data)[names(data) == 'Countries'] <- 'country'
data <-filter(data, country != 'American Samoa',country != 'Andorra', country !='Anguilla', country != 'Antigua and Barbuda', country != 'Aruba',country != 'Bahrain' , country != 'Barbados',country != 'British Virgin Islands',country != 'Cape Verde', country !='Cayman Islands' ,country != 'Comoros',country != 'Cook Islands', country != 'Dominica',country != 'Faroe Islands',country != 'French Polynesia', country !='Gibraltar', country !='Grenada',country != 'Guam', country != 'Guernsey', country != 'Hong Kong', country !='Isle of Man',country != 'Jersey', country !='Kiribati', country !='Liechtenstein',country != 'Macau', country !='Maldives', country != 'Marshall Islands',country != 'Mauritius',country !=  'Micronesia',country != 'Monaco', country !='Montserrat',country != 'Nauru', country != 'Northern Mariana Islands',country != 'Palau', country != 'Saint Helena', country != 'Saint Kitts and Nevis',country != 'Saint Lucia', country != 'Saint Pierre and Miquelon', country != 'Saint Vincent and the Grenadines', country != 'Samoa', country != 'San Marino', country != 'Sao Tome and Principe', country != 'Seychelles', country != 'Singapore', country != 'Sint Maarten', country != 'Tonga', country != 'Turks and Caicos Islands', country != 'Tuvalu', country != 'Virgin Islands', country != 'Wallis and Futuna')

data$country <- revalue(data$country, c("Bahamas" = "The Bahamas","Burma" = "Myanmar","Congo, Democratic Republic of the" = "Democratic Republic of the Congo","Congo, Republic of the" = "Republic of the Congo","Cote d'Ivoire" = "Ivory Coast","Guinea-Bissau" = "Guinea Bissau", "United States" = "United States of America", "Tanzania" = "United Republic of Tanzania"))
```

```{r include=FALSE}
# Create a custom theme for the plots. 
custom_theme <- hc_theme(
  colors = c('#5CACEE', 'green', 'red'),
  chart = list(
         backgroundColor = '#FAFAFA', 
         plotBorderColor = "black"),
  xAxis = list(
         gridLineColor = "E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         title = list(style = list(color = "#333333"))), 
  yAxis = list(
         gridLineColor = "#E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         tickWidth = 1, 
         title = list(style = list(color = "#333333"))),   
  title = list(style = list(color = '#333333', fontFamily = "Lato")),
  subtitle = list(style = list(color = '#666666', fontFamily = "Lato")),
  legend = list(
         itemStyle = list(color = "#333333"), 
         itemHoverStyle = list(color = "#FFF"), 
         itemHiddenStyle = list(color = "#606063")), 
  credits = list(style = list(color = "#666")),
  itemHoverStyle = list(color = 'gray'))
```

<style>
.colored {
  background-color: #FAFAFA;
}
</style>

GDP
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### World Map by GDP.PPP
```{r fig.height=3.5}
# Create a tibble with country and GDP
country_tibble <- data %>%
  select(country, GDP.PPP, Population)

# Create interactive world map.
highchart() %>%
  hc_add_series_map(worldgeojson, country_tibble, value = "GDP.PPP", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "GDP by Country") %>% 
  hc_subtitle(text = "Countries by GDP PPP") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = " GDP PPP") %>% 
  hc_add_theme(custom_theme)

```

### World Map by GDP Per Capita
```{r fig.height=3.5}
# Create a tibble with country and GDP
country_tibble_G <- data %>%
  select(country, GDP.PPP.Per.Capita...., Population)

# Create interactive world map.
highchart() %>%
  hc_add_series_map(worldgeojson, country_tibble_G, value = "GDP.PPP.Per.Capita....", joinBy = c('name','country')) %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "GDP Per Capita by Country") %>% 
  hc_subtitle(text = "Countries by GDP Per Capita") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = " GDP Capita") %>% 
  hc_add_theme(custom_theme)
```

Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
# Create tibble for country bar
country_bar <- data %>%
  select(country, GDP.PPP, Population) %>%
  group_by(country) %>%
  arrange(desc(GDP.PPP))

# Create interactive bar plot
highchart() %>%
  hc_add_series(country_bar, hcaes(x = country, y = GDP.PPP, color = GDP.PPP), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste("GDP: <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "GDP by country") %>% 
  hc_xAxis(categories = country_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "GDP by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)

```


### Treemap
```{r fig.height=3.5}
#Creating Treemap
hctreemap2(data = data,
           group_vars = "country",
           size_var = "GDP.PPP",
           color_var = "GDP.PPP",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            Pop: {point.value:,.0f}<br>
                            GDP: {point.valuecolor:,.0f}")
```


Continent
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
### Continent Map by GDP
```{r fig.height=3.5}

map_data <- download_map_data("custom/world-continents")

# Create a tibble for continent.
continent_tibble <- data %>%
  select(Continent, GDP.PPP) %>%
  group_by(Continent) 

# Create continent map with suicide data. 
highchart() %>%
  hc_add_series_map(map_data, continent_tibble, value = "GDP.PPP", joinBy = c('name','Continent'), name = "GDP by Continent")  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "GDP by Continent") %>%
  hc_subtitle(text= "GDP PPP of Continents") %>%
  hc_tooltip(borderWidth = 1.5,headerFormat = "", valueSuffix = '') %>%
  hc_add_theme(custom_theme)

```

Row {.tabset .tabset-fade}
-------------------------------------
### Africa
```{r fig.height=3.5}
hcmap(map = "custom/africa",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```

### Asia
```{r fig.height=3.5}
hcmap(map = "custom/asia",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```

### Europe
```{r fig.height=3.5}
hcmap(map = "custom/europe",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```

### North America
```{r fig.height=3.5}
hcmap(map = "custom/north-america",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```

### Oceania
```{r fig.height=3.5}
hcmap(map = "custom/oceania",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```

### South America
```{r fig.height=3.5}
hcmap(map = "custom/south-america",
      download_map_data = getOption("highcharter.download_map_data"),
      data = data, value = "GDP.PPP", joinBy = c('name','country'))
```


Population
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
### World Map by Population
```{r fig.height=3.5}
# Create a tibble with country and GDP
country_tibble <- data %>%
  select(country, GDP.PPP, Population)

# Create interactive world map.
highchart() %>%
  hc_add_series_map(worldgeojson, country_tibble, value = "Population", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "Population by Country") %>% 
  hc_subtitle(text = "Countries by Population") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "Population") %>% 
  hc_add_theme(custom_theme)

```


Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
# Create tibble for country bar
country_bar <- data %>%
  select(country, GDP.PPP, Population) %>%
  group_by(country) %>%
  arrange(desc(Population))

# Create interactive bar plot
highchart() %>%
  hc_add_series(country_bar, hcaes(x = country, y = Population, color = Population), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste("Population: <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Population by country") %>% 
  hc_xAxis(categories = country_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Population by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```


### Treemap Asia
```{r fig.height=3.5}
#Creating Treemap
Treemap_Asia <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="Asia") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_Asia,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

### Treemap Africa
```{r fig.height=3.5}
#Creating Treemap
Treemap_Africa <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="Africa") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_Africa,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

### Treemap Europe
```{r fig.height=3.5}
#Creating Treemap
Treemap_Europe <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="Europe") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_Europe,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

### Treemap Oceania
```{r fig.height=3.5}
#Creating Treemap
Treemap_Oceania <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="Oceania") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_Oceania,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

### Treemap North America
```{r fig.height=3.5}
#Creating Treemap
Treemap_NA <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="North America") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_NA,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

### Treemap South America
```{r fig.height=3.5}
#Creating Treemap
Treemap_SA <- data %>%
  select(country,GDP.PPP, Population,Continent) %>%
  filter(Continent=="South America") %>%
  group_by(Population) %>%
  arrange(desc(Population))

hctreemap2(data = Treemap_SA,
           group_vars = "country",
           size_var = "Population",
           color_var = "GDP.PPP",
           type = "value",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_add_theme(custom_theme) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Pop: {point.value:,.0f}<br>
             GDP: {point.colorValue:,.0f}")
```

Urban
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
###  Urban Population of countries
```{r fig.height=3.5}
# Create a tibble for urban population
urban_tibble <- data %>%
  select(country, Urban, GDP.PPP) %>%
  #summarise(Urbanpop = Urban*100 ) %>%
  group_by(Urban) 

highchart() %>%
  hc_add_series_map(worldgeojson, urban_tibble, value = "Urban", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Urban Population by Country") %>% 
  hc_subtitle(text = "Countries by their urban population") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "") %>% 
  hc_add_theme(custom_theme)
```


Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
# Create tibble for Urban bar
Urban_bar <- data %>%
  select(country, Urban, Population) %>%
  group_by(Urban) %>%
  arrange(desc(Urban))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Urban_bar, hcaes(x = country, y = Urban, color = Urban), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste("Urban: <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Urban Population by Country") %>% 
  hc_xAxis(categories = Urban_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Urban Population by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)

```

Health Expenditure as part of GDP
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
###  Health Exprenditure of countries by GDP
```{r fig.height=3.5}
# Create a tibble for Health Expenditure
Health_tibble <- data %>%
  select(country, Health.Expenditure.as.Part.of.GDP, GDP.PPP) %>%
  group_by(Health.Expenditure.as.Part.of.GDP) 

highchart() %>%
  hc_add_series_map(worldgeojson, Health_tibble, value = "Health.Expenditure.as.Part.of.GDP", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Health Exprenditure of countries by GDP") %>% 
  hc_subtitle(text = "Countries by their Health Exprenditure") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = " %") %>% 
  hc_add_theme(custom_theme)
```

Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
# Create tibble for Health bar
Health_bar <- data %>%
  select(country, Health.Expenditure.as.Part.of.GDP, Population) %>%
  group_by(Health.Expenditure.as.Part.of.GDP) %>%
  arrange(desc(Health.Expenditure.as.Part.of.GDP))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Health_bar, hcaes(x = country, y = Health.Expenditure.as.Part.of.GDP, color = Health.Expenditure.as.Part.of.GDP), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste("GDP: <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "GDP by country") %>% 
  hc_xAxis(categories = Health_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "GDP by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)

```


Migration Rate
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
###  Migration Rate of countries

```{r fig.height=3.5}
# Create a tibble for Net Migration population
migration_tibble <- data %>%
  select(country, Net.Migration.Rate, GDP.PPP) %>%
  group_by(Net.Migration.Rate) 

highchart() %>%
  hc_add_series_map(worldgeojson, migration_tibble, value = "Net.Migration.Rate", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Migration by Country") %>% 
  hc_subtitle(text = "Countries by their Migration  rate") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "") %>% 
  hc_add_theme(custom_theme)
```


Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
Migaration_bar <- data %>%
  select(country,Net.Migration.Rate , Population) %>%
  group_by(Net.Migration.Rate) %>%
  arrange(desc(Net.Migration.Rate))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Migaration_bar, hcaes(x = country, y = Net.Migration.Rate, color = Net.Migration.Rate), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Migration by country") %>% 
  hc_xAxis(categories = Migaration_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Migration by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Adult Obesity Rate
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
###  Adult Obesity Rate of countries

```{r fig.height=3.5}
# Create a tibble for Adult Obesity 
AO_tibble <- data %>%
  select(country, Adult.Obesity.Rate, GDP.PPP) %>%
  group_by(Adult.Obesity.Rate) 

highchart() %>%
  hc_add_series_map(worldgeojson, AO_tibble, value = "Adult.Obesity.Rate", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Adult Obesity by Country") %>% 
  hc_subtitle(text = "Countries by their Adult Obesity  rate") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "") %>% 
  hc_add_theme(custom_theme)
```


Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
AO_bar <- data %>%
  select(country,Adult.Obesity.Rate , Population) %>%
  group_by(Adult.Obesity.Rate) %>%
  arrange(desc(Adult.Obesity.Rate))

# Create interactive bar plot
highchart() %>%
  hc_add_series(AO_bar, hcaes(x = country, y = Adult.Obesity.Rate, color = Adult.Obesity.Rate), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Adult Obesity by country") %>% 
  hc_xAxis(categories = Migaration_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Adult Obesity by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Life Expectancy
=======================================================================
Row {data-height=650}
-----------------------------------------------------------------------
###  Life Expectancy years by countries

```{r fig.height=3.5}
# Create a tibble for Life 
L_tibble <- data %>%
  select(country, Life.Expectancy..years., GDP.PPP) %>%
  group_by(Life.Expectancy..years.) 

highchart() %>%
  hc_add_series_map(worldgeojson, L_tibble, value = "Life.Expectancy..years.", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Life Expectancy by Country") %>% 
  hc_subtitle(text = "Countries by their Life Expectancy") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "") %>% 
  hc_add_theme(custom_theme)
```


Row {.tabset .tabset-fade}
-------------------------------------
### Barplot
```{r fig.height=3.5}
L_bar <- data %>%
  select(country,Life.Expectancy..years. , Population) %>%
  group_by(Life.Expectancy..years.) %>%
  arrange(desc(Life.Expectancy..years.))

# Create interactive bar plot
highchart() %>%
  hc_add_series(L_bar, hcaes(x = country, y = Life.Expectancy..years., color = Life.Expectancy..years.), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Life Expectancy years by country") %>% 
  hc_xAxis(categories = L_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Life Expectancy by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Sector Combination
=======================================================================
Row {.tabset .tabset-fade}
-------------------------------------
### Agriculture
```{r fig.height=3.5}
# Create a tibble for Agriculture 
Agri_tibble <- data %>%
  select(country,Agriculture , GDP.PPP) %>%
  group_by(Agriculture) 

highchart() %>%
  hc_add_series_map(worldgeojson, Agri_tibble, value = "Agriculture", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Agriculture Sector by Country") %>% 
  hc_subtitle(text = "Countries by their Agriculture Sector") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "%") %>% 
  hc_add_theme(custom_theme)
```

### Barplot
```{r fig.height=3.5}
Agri_bar <- data %>%
  select(country,Agriculture , Population) %>%
  group_by(Agriculture) %>%
  arrange(desc(Agriculture))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Agri_bar, hcaes(x = country, y = Agriculture, color = Agriculture), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Agriculture Sector by country") %>% 
  hc_xAxis(categories = Agri_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Agriculture by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Row {.tabset .tabset-fade}
-------------------------------------
### Service
```{r fig.height=3.5}
# Create a tibble for Service 
Service_tibble <- data %>%
  select(country,Service , GDP.PPP) %>%
  group_by(Service) 

highchart() %>%
  hc_add_series_map(worldgeojson, Service_tibble, value = "Service", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Service Sector by Country") %>% 
  hc_subtitle(text = "Countries by their Service Sector") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "%") %>% 
  hc_add_theme(custom_theme)
```

### Barplot
```{r fig.height=3.5}
Service_bar <- data %>%
  select(country,Service , Population) %>%
  group_by(Service) %>%
  arrange(desc(Service))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Service_bar, hcaes(x = country, y = Service, color = Service), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Service Sector by country") %>% 
  hc_xAxis(categories = Service_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Agriculture by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Row {.tabset .tabset-fade}
-------------------------------------
### Industry
```{r fig.height=3.5}
# Create a tibble for Industry 
Industry_tibble <- data %>%
  select(country,Industry , GDP.PPP) %>%
  group_by(Industry) 

highchart() %>%
  hc_add_series_map(worldgeojson, Industry_tibble, value = "Industry", joinBy = c('name','country'))  %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_colorAxis(minColor = "#C5C889", maxColor = "#434348") %>% 
  hc_title(text = "Industry Sector by Country") %>% 
  hc_subtitle(text = "Countries by their Industry Sector") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = "%") %>% 
  hc_add_theme(custom_theme)
```

### Barplot
```{r fig.height=3.5}
Industry_bar <- data %>%
  select(country,Industry , Population) %>%
  group_by(Industry) %>%
  arrange(desc(Industry))

# Create interactive bar plot
highchart() %>%
  hc_add_series(Industry_bar, hcaes(x = country, y = Industry, color = Industry), type = "bar")  %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste(": <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Industry Sector by country") %>% 
  hc_xAxis(categories = Industry_bar$country, 
           labels = list(step = 1),
           min = 0, max = 25,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Industry by Country")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5)) %>% 
  hc_add_theme(custom_theme)
```

Conculsion
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
###  Coorelation Matrix
```{r fig.height=7}

#Correlation Matrix
data.df <- data %>%
  select_if(is.numeric) %>%
  cor(.)

hchart(cor(data.df))

```

###  Principal Components
```{r fig.height=10}
hchart(princomp(data.df, cor = TRUE))

```

###  Heatmap
```{r fig.height=10}
heatmap(data.df, Colv = NA, Rowv = NA, scale="column", main="Heatmap")

```
